%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{fontawesome}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{listofitems}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumePositionChange}[2]{
  \vspace{-\baselineskip}\item%
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}%
      \textit{\small#1} & \textit{\small #2} \\%
    \end{tabular*}\vspace{-5pt}%
}

\newcommand{\resumeProject}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[label=, leftmargin=0em]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{center}
  {\LARGE \textbf{Ryan Looney}} \\
  \vspace{2pt}
  \renewcommand{\arraystretch}{1.5}
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}c}
        \faMapMarker\hspace{2pt} Boston, MA \hspace{24pt} 
        \faEnvelope\hspace{2pt} \href{mailto:looney.r@northeastern.edu}{looney.r@northeastern.edu} \hspace{24pt} 
        \faMobile\hspace{2pt} (203) 917-7516 \hspace{24pt} 
        \faLinkedinSquare\hspace{2pt} \href{https://www.linkedin.com/in/ryan-looney-5773b113a/}{linkedin.com/ryan-looney} \\
    \end{tabular*}
\end{center}

%-----------EDUCATION-----------------
\vspace{-10pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northeastern University}{Boston, MA}
      {MS in Computer Science; GPA: 3.76}
      {Sep 2021 - May 2024}

            {    
            \begin{tabular}{@{}p{2.5cm}p{10cm}}
                Coursework: & Algorithms, Discrete Mathematics, Object-Oriented Design, \\
                & \hangindent=2.5em Computer Systems, Web Development
            \end{tabular}
            }
    \resumeSubheading
      {Penn State University}{University Park, PA}
      {BS in Management Information Systems; GPA: 3.49}{Aug 2015 - May 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Quickbase}{Boston, MA}
      {Software Engineer Co-op}{Jan 2023 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Working in a team of 4 engineers, developed a customer-ready interactive data table feature in React to replace the C++ legacy version of the feature, resulting in additional functionality (such as dynamic sorting and filtering), and an improved user interface.}
        \resumeItem{}
          {Developed software in an Agile framework using Jira, Git, and Jenkins, resulting in discrete and traceable code releases .}
        \resumeItem{}
         {Developed extensible test suites using Jest and Enzyme for each Jira story, with all tests exceeding 90\% global coverage.}
      \resumeItemListEnd

      

    \resumeSubheading
       {Northeastern University}{Boston, MA}
       {Teaching Assistant}{May 2022 - Aug 2022}
       \resumeItemListStart
            \resumeItem{}
                {Held regular office hours to help students debug assignments, reviewed class concepts such as data structures and algorithms in detail, and assisted in configuring their Linux machines and Vim editors, resulting in overall educational enrichment.}
       \resumeItemListEnd

    \resumeSubheading
      {Epic Systems}{Verona, WI}
      {Application Manager}{Jan 2021 - July 2021}
        \resumeItemListStart
            \resumeItem{}
            {Led Epic software implementation at a dentistry practice in CA on an accelerated 4.5-month timeline.}
            \resumeItem{}
            {Assembled and validated robust software implementation project plans with client executives, resulting in a low-ticket go-live. }
            \resumeItem{}
            {Mentored and supervised the project Application Coordinator, providing guidance on project tasks, software functionality, and best practices, resulting in their promotion to Application Manager upon completion of the project.}
      \resumeItemListEnd
    \resumePositionChange{Application Coordinator}{Sep 2019 - July 2021}
        \resumeItemListStart
            \resumeItem{}
                {Lead application-specific legacy data conversion efforts, working with a multi-disciplinary team of SMEs exceeding project timelines.}
            \resumeItem{}
                {Developed, improved upon, and maintained implementation tools and software content for the Orthopedics, Dermatology, and Ophthalmology software modules to be used in implementing medical best practices at over 400 hospital systems, }
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProject{YNAB Analysis Web App}{Personal}
            \resumeItemListStart
                \resumeItem{}
                    {Visualized personal financial data on a variety of dimensions using React, Redux, Axios, and the PlotlyJS library.}
            \resumeItemListEnd
    \resumeProject{Thunderdome Simulation Project}{Northeastern University / Personal}
        \resumeItemListStart
            \resumeItem{}
                {Battle Simulation repeatedly pits two user-chosen characters against one another in a fictional “Thunderdome” battle arena.}
            \resumeItem{}
                {Re-wrote a class project from scratch in Java to embody good principles of object-oriented design (MVC, Polymorphism, D.R.Y).}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: JavaScript \textbar{} Python \textbar{} Java \textbar{} C/C++  \textbar{} CSS \textbar{} HTML \textbar{} Linux Terminals (Bash, zsh) \textbar{} SQL}
   }
   \item{
      \textbf{Other Technologies:} React \textbar{} Styled Components \textbar{} NodeJS \textbar{} PlotlyJS \textbar{} Pandas \textbar{} Jenkins \textbar{} Git \& GitHub
    }
 \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
